%!TEX root = ../dissertation.tex

% Acknowledgments: This one is optional
\chapter*{Acknowledgments}
% Thanks to everyone and bla bla bla
First and foremost, I would like to thank Professor Alexandre Bernardino for conceding me the opportunity of working alongside him for the last one year and a half in this project. Professor Alexandre genuinely dedicates himself to his work, to science and to helping others around him achieve their own goals and ambitions. In him, I have found comfort and great role model. Both him and Professor José Santos-Victor should feel proud for keeping such a warm and friendly working environment at Vislab.

Professor John Van Opstal is the brain (and the eye) behind the ORIENT project. I thank him for the great amount of time he has dispensed on helping our team in Lisbon, even when it's not his area of expertise. I seek inspiration in him, as every time he talks about a topic, he does it with enormous passion, confidence and happiness. He infects everyone else in the room with the same enthusiasm as he has for life.

The last piece of the project are my teammates, Carlos and Akhil that made everything much more wholesome by supporting, helping and making me laugh on the toughest nights. They are the most competent people I have met and I have no doubt they will succeed in any path they choose to follow as I stand to support them onto it. To the most recent members, Rui and Bernardo, I wish you all the luck and hope you enjoy the experience as much as I have.\\

In the day I arrived to Técnico, Professor Arlindo emphasized how the next five years would be the best of my life and he was right. But, he was right because during this time I have met the most incredible humans and collected  numerous memories I hold very dear to my heart. I thank that to my group of friends that have kept by my side from the beginning and with whom I could not have done it, Firmino, João, Sara, Marco and Pedro. I wish to see you happy, fulfilled and on the next monthly dinner with enough alcohol in your blood.\\

As it should be implicit to them, I want to hugely thank my family and Bruno that through a lot of trouble down the road, have, nevertheless, always supported me in doing what I find suiting in my path.\\ 

Lastly, it feels right to mention my cat, Panda Félix, that through cruel punishments that consist of wrist and ankles biting, bowl throwing and alternative home decorations, has always looked for comfort and cuddles in me and I in him during tough times.\\

You all will be missed.







