% Glossary Definition

\newglossaryentry{homo}
{	
	name={homogeneous coordinates}, 
	description={In computer vision, an extra dimension is added to the coordinates of a point that makes perspective projection transformations easier to compute. For a point $[x \ y]^T$, any three numbers, $[a_1 \ a_2 \ a_3]^T$ for which $\frac{a_1}{a_3} = x$ and $\frac{a_2}{a_3} = y$ are homogenous coordinates. This three new coordinates are represented by "$\sim$", e.g. $\widetilde{a} = [a_1 \ a_2 \ a_3]^T$}
}

\newglossaryentry{gauss}
{	
	name={gaussian blur}, 
	description={The Gaussian blur is an image-blurring filter that uses a Gaussian function. It produces a smoother and less noisy image.}
}

\newglossaryentry{svd}
{
	name={singular value decomposition},
	description={\acrfull{svdd} is  the  factorization  of a matrix A into  the product of three matrices $U$$\Sigma$$V^T$   where the columns of $U$ and $V$ are orthonormal and $\Sigma$ is a diagonal matrix with positive real entries}
}

\newglossaryentry{skews}
{
	name={skew symmetric matrix},
	description={A skew-symmetric matrix is a square matrix whose transpose equals its negative. These matrices can be used to represent cross products as matrix multiplications. If $\mathbf{\tilde{l}} = \mathbf{\tilde{p}} \times \mathbf{\tilde{q}}$, it may be written as $\mathbf{\tilde{l}} = [\mathbf{\tilde{p}}]_{\times} \mathbf{\tilde{q}}$, where $[\mathbf{p}]_{\times}$ is a skew symmetric matrix defined as
	\begin{equation}
		\left[ \begin{array} { c c c } { 0 } & { - p_ { 3 } } & { p_{ 2 } } \\ { p_{ 3 } } & { 0 } & { - p_{ 1 } } \\ { - p _ { 2 } } & { p_ { 1 } } & { 0 } \end{array} \right]
	\end{equation}}
}

\newglossaryentry{lag}
{
	name={langrange multipliers},
	description={Using lagrange multipliers is a strategy to find the minima or maxima of a function subject to equality constraints. This works by converting the constrained problem into a form such that the derivative test of an unconstrained problem can still be applied. The lagrangian form of a a function $f(x)$ subject to $g(x) = 0$ would be $\mathcal{L}(x, \lambda)=f(x)+\lambda g(x)$}
}

